Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-23 manuscript/ERL_global_C_review.Rmd
switched to pulling C cycle diagrams from ForC
#23 -
@ValentineHerr , you don't need to save the diagrams in the ERL repo now-- just ForC is fine.

Susan Cook-Patton

@@

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; National Zoological Park, Front Royal, VA 22630, USA
2. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama

@@

  knitr::include_graphics("tables_figures/Tropical broadleaf MATURE.png")
```

@@

  knitr::include_graphics("tables_figures/Temperate broadleaf MATURE.png")
```

@@

  knitr::include_graphics("tables_figures/Temperate conifer MATURE.png")
```

@@

  knitr::include_graphics("tables_figures/Boreal conifer MATURE.png")
```
\elandscape

@@

  knitr::include_graphics("tables_figures/Tropical broadleaf YOUNG.png")
```

@@

  knitr::include_graphics("tables_figures/Temperate broadleaf YOUNG.png")
```

@@

  knitr::include_graphics("tables_figures/Temperate conifer YOUNG.png")
```

@@

  knitr::include_graphics("tables_figures/Boreal conifer YOUNG.png")
```
\elandscape

>>>>

Susan C. Cook-Patton^5^

@@

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; National Zoological Park, Front Royal, VA 22630, USA
2. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama
3.
4.
5. The Nature Conservancy, Arlington VA 22203
6.

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/Tropical broadleaf MATURE.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/Temperate broadleaf MATURE.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/Temperate conifer MATURE.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/Boreal conifer MATURE.png")
```
\elandscape

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/Tropical broadleaf YOUNG.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/Temperate broadleaf YOUNG.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/Temperate conifer YOUNG.png")
```

@@

  knitr::include_graphics("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/C_cycle_diagrams/Diagrams/Boreal conifer YOUNG.png")
```
\elandscape
